When Cities Change Hands: Extinctions of Dynasties and \\Breaks in Development

### 2023-01-20 paper/paper.tex
test citations and shorten labels
more paper experiments
add new ideas for titles

\title{Territory size, governance and economic performance: \\Evidence from German dynasties}
\author{Elias Hadj Ammar}
\date{January 2023}

\begin{document}

\maketitle
\thispagestyle{empty}

Alternative title ideas: 
\begin{itemize}
    \item "Good riddance? What happens to states when dynasties go extinct" - catchy, but obscure, and also not what the paper is about.
    \item "What kind of ruler makes states prosper?" "The best kind of autocrat?"
    \item "How individual dynasties in the HRE promoted or hindered growth" - to the point, but detached from literature.
    \item Winners and losers
    \item Good riddance
    \item Thinly veiled dick joke
    \item Preview of results
\end{itemize}

@@

This is like \cite{alesinaS1997}

>>>>

\title{When Cities Change Hands: Extinctions of Dynasties and \\Breaks in Development}
\author{Elias Hadj Ammar}
\date{January 2023}

\begin{document}
\maketitle
\footnote{I gratefully acknowledge helpful comments from Davide Cantoni, Matthias Weigand, and my fellow research assistants at the Chair of Economic History.}
Keep in mind that the title doesn't need to say everything. It needs to be catchy and it needs to be not-misleading about the core of the paper.
Alternative title ideas: 
\begin{itemize}
    \item "Good riddance? What happens to states when dynasties go extinct" - catchy, but obscure, and also not what the paper is about.
    \item "What kind of ruler makes states prosper?" "The best kind of autocrat?"
    \item ``Territory size, leaders and economic development: Evidence from German dynasties'' {Leaders, territory size and growth: Evidence from extinctions of German dynasties}

    \item "How individual dynasties in the HRE promoted or hindered growth" - to the point, but detached from literature.
    \item Winners and losers
    \item Good riddance
    \item Thinly veiled dick joke about size
    \item Preview of results
    \item Which country you belong to / ``When cities change hands''
    \item {Extinctions of dynasties and changes in development}
    \item {When Cities Change Hands: Extinctions of Dynasties and Changes in Development}
    \item Family Affair / Family Matters / Family Business / something more fitting about families
    \item Successions and success
    \item {Family Matters: Extinctions of Dynasties and Changes in Development}
    \item something about game of thrones / a silly pun
\end{itemize}

@@

This is like \cite{as1997} and \cite{aw1998} and also \cite{as1997} and also \cite{olken2005}. hi there \cite{olken2005}
